### 2017-08-07 doc/MSc-dissertation.tex
Kazantsev theory

An important distinction that

Since turbulent MHD encompasses problems from vastly different nature, for the purpose of this dissertation, the focus will be centered on forced, non-helical, incompressible, homogeneous, isotropic MHD turbulence. This problem dates back to Batchelor, who determined that for non-helical turbulence the small scale components of the velocity field have the most influence on the magnetic field~\cite{batchelor1950spontaneous}. Since HIT is being considered, then it is not possible to have a mean magnetic field, $\langle \bm B \rangle = 0$. This means that the magnetic field in play is a fluctuating component $\bm b$ generated by a turbulent dynamo.

>>>>

An important distinction that is made regarding the length scales at which the magnetic fields generated by dynamo action. Those created by material flow in Earth's outer core are coherent in large spatial scales and are thus dubbed large-scale dynamos (LSD). On the other hand, when a dynamo's generated magnetic field exist at spatial scales smaller than the energy-carrying eddied, then it is called a small-scale dynamo (SSD). This distinction is important as the SSD exists only for large values of magnetic Reynolds number $Re_M \gg 1$. In the particular case of isotropic turbulence, the distinction between SSD and LSD action is intimately tied with the kinetic helicity of the system. Namely, non-helical flows \textit{can} spawn SSD action, whereas LSD action arises in helical flows - which is why $\alpha$-effect is exclusively a LSD effect.

Since turbulent MHD encompasses problems from vastly different nature, for the purpose of this dissertation, the focus will be centered on forced, non-helical, incompressible, homogeneous, isotropic MHD turbulence. This problem dates back to Batchelor, who determined that for non-helical turbulence the small scale components of the velocity field have the most influence on the magnetic field~\cite{batchelor1950spontaneous}. Since HIT is being considered, then it is not possible to have a mean magnetic field, $\langle \bm B \rangle = 0$. This means that the magnetic field in play is a fluctuating component $\bm b$ generated by a turbulent dynamo. The problem of the small-scale dynamo then is being studied here.

\subsubsection{Kazantsev theory}

In turbulent enough flow, constituent particles randomly ``walk'' away from each other with time. A magnetic field line that is frozen into the fluid will then be stretched by the particles' movement (stretching in eqn.~\ref{eq3.1} is the term $(\bm b \cdot \bm \nabla)\bm u$). In time, this will lead to an increase in the magnetic field if the fluid is incompressible. As $\bm b$ increases Ohmic dissipation increases until a balance is reached with the growth from this random stretching. This was studied (for non-helical flows) by Kazantsev, who found that in certain circumstances dynamo action could be achieved. He did so by first considering HIT in MHD and random, gaussian, velocity and magnetic fields with zero mean fields $\delta$-correlated in time.

Afterwards, equations for the equal time two-point correlation functions of the velocity and magnetic fields allowed him to derive an equation for the two-point correlation function of the magnetic field for non-helical HIT. Using that, a Schroedinger-type time independent equation arose. These showed the possibility of bound states, provided a critical magnetic Reynolds number $Re_M^{crit}$ within the range [30:60] was reached, which meant that a small-scale dynamo was being excited~\cite{brandenburg2005astrophysical}.

\iffalse
The equal time two-point correlation function of the velocity field is then required to be described by $C_{ij}^{uu}(\bm r, t)=T_{ij}(r)$, where $T_{ij}(r)$ has to be of the form of eqn.~\ref{eq3.10} ($T_N(r)$ and $T_L(r)=C_{LL}^{uu}(r)$ are the transverse and longitudinal correlation functions of the velocity field, respectively).

\begin{align}
 T_{ij}(r) &= \left( \delta_{ij} - \frac{r_i r_j}{r^2} \right) T_N(r) + \frac{r_i r_j}{r^2} T_L(r) \label{eq3.10} \\
 T_N(r)&=\frac{1}{2r}\frac{\partial}{\partial r} \left[r^2 T_L(r) \right], \qquad \qquad\text{if }\bm \nabla \cdot \bm u = 0  \nonumber
\end{align}

Since similar considerations were made for the magnetic field (and $\bm \nabla \cdot \bm b = 0$ is one of Maxwell equations) the equal time two-point correlation function of $\bm b$ is $C_{ij}^{bb}(\bm r, t) = M_{ij}(r)$, defined by eqn.~\ref{eq3.11}, for which $M_N(r)$ is the transverse correlation function of the magnetic field and $M_L(r)=C_{LL}^{bb}(r)$ is that of the longitudinal magnetic field.

\begin{align}
 M_{ij}(r) &= \left( \delta_{ij} - \frac{r_i r_j}{r^2} \right) M_N(r) + \frac{r_i r_j}{r^2} M_L(r) \label{eq3.11} \\
 M_N(r)&=\frac{1}{2r}\frac{\partial}{\partial r} \left[r^2 M_L(r) \right] \nonumber
\end{align}

\fi
